Dominance Regions for Imaginary $\bfg$-vectors

### 2022-02-14 dominance_regions.tex
More equation massaging
Fixed inequalities

  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following six inequalities:
  \begin{align}
    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
  \end{align}
  Are any of these better forms?
  \begin{align}
    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
    \\
    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
  \end{align}
  Another proposal (I also changed the order of the equations)
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}
  Maybe this one:
  \begin{align}
    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
    \\
    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
    \\
    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
    \\
    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
    \\
    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
    \\
    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
  \end{align}

>>>>

%  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by the following inequalities:
%  \begin{align}
%    -\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1+\lambda_2-\frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
%    \\
%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1 - \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}x-y\geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x-\frac{b c+\sqrt{b c (b c-4)}}{2 c}y\geq0
%    \\
%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}\lambda_1-\frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}x-y\geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}-2}{2}\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2 c}\lambda_2+x+\frac{b c-\sqrt{b c (b c-4)}}{2 c}y\geq0
%  \end{align}
%  Are any of these better forms?
%  \begin{align}
%    (x-\lambda_1)+\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
%    \\
%    \nonumber \iff \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2)\geq0
%    \\
%    -\frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
%    \\
%    \nonumber \iff -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
%    \\
%    -\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2 + \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
%    \\
%    \nonumber \iff -b\lambda_2 + (x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+(x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
%    \\
%    \nonumber \iff c\lambda_1+\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
%    \\
%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_2-\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)\geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}}{2}\lambda_1+b\lambda_2+(x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)\geq0
%  \end{align}
%  Another proposal (I also changed the order of the equations)
%  \begin{align}
%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
%    \\
%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
%    \\
%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
%    \\
%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
%    \\
%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
%  \end{align}
%  Maybe this one:
%  \begin{align}
%    \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq0
%    \\
%    \frac{b c+\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1-b\lambda_2)-(y-\lambda_2) & \geq 0
%    \\
%    -\frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)& \geq c\lambda_1+\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
%    \\
%    -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2)& \geq0
%    \\
%    (x-\lambda_1)-\frac{b c+\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2-c\lambda_1) & \geq 0
%    \\
%    (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
%  \end{align}
%
%  Yet another version:
% 
% {
%    \everymath={\displaystyle}
%  \[
%  \begin{array}{rcccl}
%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
%    \\
%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
%    \\
%    - b \lambda_2 & \geq & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) 
%    \\
%    0 & \geq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \geq &-\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2
%  \end{array}
%\]
%}
%
%Or: (Maybe at this point we can remove $c/c$ and $b/b$)
%
% {
%    \everymath={\displaystyle}
%  \[
%  \begin{array}{rcccl}
%    -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2 & \geq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \geq & 0
%    \\
%    &  & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \geq & c\lambda_1
%    \\
%    -\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1-b\lambda_2  & \leq & (x-\lambda_1)+\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & 0
%    \\
%    & & - (x-\lambda_1) + \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)  & \leq & - b \lambda_2
%  \end{array}
%\]
%}
%
%
%Or Or: (Maybe at this point we can remove $c/c$ and $b/b$)
%
%
% The following, and possibly all the one before, has a typo
% {
%    \everymath={\displaystyle}
%    \def\arraystretch{2.8}
%  \[
%  \begin{array}{rcccl}
%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
%    \\
%    c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
%    \\
%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
%    \\
%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
%  \end{array}
%\]
%}
% {
%    \everymath={\displaystyle}
%    \def\arraystretch{2.8}
%  \[
%  \begin{array}{rcccl}
%    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & -c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2
%    \\
%    -c\lambda_1 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2)
%    \\
%    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2
%    \\
%    b \lambda_2 & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2)
%  \end{array}
%\]
%}
  The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
 {
    \everymath={\displaystyle}
    \def\arraystretch{2.8}
  \[
  \begin{array}{rcccl}
    0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
    \\
    \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
    \\
    0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
    \\
    \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
  \end{array}
\]
}
